### 2024-08-24 my_paper/tables/maineffect-proxy.tex
edits

\begin{table}[H]

\caption{Main Effect of Proxy on Second-Generation's Hispanic Self-identification \label{tab:hispbyproxy}}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[c]{>{}lllll}
\toprule
Parents Type & All & Hispanic-Hispanic & Hispanic-White & White-Hispanic\\
\midrule
\textbf{Proxy:} &  &  &  & \\
\hspace{1em}\textbf{Mother} & 0.94 & 0.96 & 0.9 & 0.84\\
\hspace{1em}\textbf{Father} & 0.92 & 0.96 & 0.86 & 0.8\\
\hspace{1em}\textbf{Self} & 0.96 & 0.97 & 0.9 & 0.84\\
\hspace{1em}\textbf{Others} & 0.96 & 0.97 & 0.92 & 0.9\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Main Effect of Proxy on Second-Generation's Asian Self-identification \label{tab:hispbyproxy}}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[c]{>{}lllll}
\toprule
Parents Type & All & Asian-Asian & Asian-White & White-Asian\\
\midrule
\textbf{Proxy:} &  &  &  & \\
\hspace{1em}\textbf{Mother} & 0.72 & 0.97 & 0.37 & 0.3\\
\hspace{1em}\textbf{Father} & 0.72 & 0.97 & 0.39 & 0.29\\
\hspace{1em}\textbf{Self} & 0.87 & 0.97 & 0.23 & 0.31\\
\hspace{1em}\textbf{Others} & 0.88 & 0.96 & 0.6 & 0.54\\
\bottomrule
\end{tabular}
\end{table}

### 2024-08-24 my_paper/tables/tab01-SumStat.tex
edits

\begin{table}[H]

\caption{Current Population Survey (CPS) Summary Statistics\label{tab:sumstat1}}
\centering
\begin{threeparttable}
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{\textbf{Overall}} & \multicolumn{3}{c}{\textbf{By Generation}} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-5}
\textbf{Characteristic} & \makecell[l]{\textbf{All Sample} \\N = 1,131,828} & \makecell[c]{\textbf{First} \\N=119,778} & \makecell[c]{\textbf{Second} \\N=761,450} & \makecell[c]{\textbf{Third} \\N=254,699}\\
\midrule
Female & 0.49 & 0.48 & 0.49 & 0.49\\
Hispanic & 0.91 & 0.96 & 0.94 & 0.82\\
Age & \makecell[c]{8.6 \\(5.1)} & \makecell[c]{11.5 \\(4.3)} & \makecell[c]{8.3 \\(5.0)} & \makecell[c]{7.9 \\(5.0)}\\
\makecell[l]{College Graduate: \\ \hspace{1em}Father} & 0.14 & 0.15 & 0.11 & 0.23\\
\makecell[l]{College Graduate: \\ \hspace{1em}Mother} & 0.14 & 0.15 & 0.11 & 0.22\\
\makecell[l]{Total Family Income \\\hspace{1em}(1999 dollars)} & \makecell[c]{39,882 \\(48,692)} & \makecell[c]{31,927 \\(38,804)} & \makecell[c]{36,726 \\(45,353)} & \makecell[c]{53,000 \\(58,984)}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{*} Mean\ \ (SD)}\\
\end{tabular}}
\begin{tablenotes}
\item[1] The sample includes children ages 17 and below who live in intact families. First-generation Hispanic immigrant children that were born in a Spanish-speaking county. Native-born second-generation Hispanic immigrant children with at least one parent born in a Spanish-speaking country. Finally, native-born third-generation Hispanic immigrant children with native-born parents and at least one grand parent born in a Spanish-speaking country.
\item[2] Data source is the 2004-2021 Current Population Survey.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering
\caption{CPS Summary Statistics with Skin IAT Scores \label{tab:sumstat1}}
\centering
\begin{threeparttable}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{\textbf{Overall}} & \multicolumn{3}{c}{\textbf{By Generation}} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-5}
\textbf{Characteristic} & \makecell[c]{\textbf{All Sample} \\N = 318,404} & \makecell[c]{\textbf{First} \\N=40,033} & \makecell[c]{\textbf{Second} \\N=199,294} & \makecell[c]{\textbf{Third} \\N=79,077}\\
\midrule
Female & 0.49 & 0.53 & 0.49 & 0.49\\
Asian & 0.65 & 0.96 & 0.73 & 0.31\\
Age & 8.4 (5.1) & 10.9 (4.5) & 8.3 (5.1) & 7.7 (5.0)\\
College Graduate:\ \ 	 Father & 0.52 & 0.59 & 0.52 & 0.50\\
College Graduate:\ \ 	 Mother & 0.52 & 0.56 & 0.51 & 0.52\\
Total Family Income\ \ 	 (1999 dollars) & 87,031 (84,797) & 75,815 (74,489) & 88,295 (88,411) & 89,436 (80,051)\\
\bottomrule
\end{tabular}}
\begin{tablenotes}
\item[1] The samples include children ages 17 and below who live in intact families. First-generation Asian immigrant children that were born in a Asian country. Native-born second-generation Asian immigrant children with at least one parent born in a Asian country. Finally, native-born third generation Asian immigrant children with native-born parents and at least one grand parent born in a Asian country.
\item[2] Data source is the 2004-2021 Current Population Survey.
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2024-08-24 my_paper/tables/tab41a-marriage.tex
edits

\begin{table}[H]

\caption{Relationship Between Bias and Interethnic Marriages \label{regtab-logit-02}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Hispanic Men} & \multicolumn{1}{c}{Hispanic Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interethnic} & \specialcell{(2) \\ Interethnic} & \specialcell{(3) \\ Interethnic}\\
\midrule
Bias & 0.05*** & 0.06*** & 0.07***\\
 & (0.01) & (0.01) & (0.01)\\
College Graduate: Wife & 0.05*** & 0.04*** & 0.04***\\
 & (0.00) & (0.00) & \vphantom{1} (0.00)\\
College Graduate: Husband & 0.08*** & 0.04*** & 0.06***\\
 & (0.00) & (0.00) & (0.00)\\
\midrule
Observations & 477,672 & 433,232 & 434,297\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interethnic}) as a
                      linear probability model.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Relationship Between Bias and Interethnic Marriages \label{regtab-logit-02}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Asian Men} & \multicolumn{1}{c}{Asian Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interethnic} & \specialcell{(2) \\ Interethnic} & \specialcell{(3) \\ Interethnic}\\
\midrule
Bias & $0.04$*** & $-0.01$ & $0.03$**\\
 & ($0.01$) & ($0.01$) & ($0.01$)\\
College Graduate: Wife & $0.04$*** & $0.04$*** & $0.05$***\\
 & ($0.00$) & ($0.01$) & \vphantom{1} ($0.00$)\\
College Graduate: Husband & $-0.01$* & $-0.01$ & $-0.02$***\\
 & ($0.00$) & ($0.01$) & ($0.00$)\\
\midrule
Observations & $69,800$ & $52,103$ & $60,214$\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interethnic}) as a
                      linear probability model.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2024-08-24 output/tables/tab01a-SumStatOverAll.tex
edits

\caption{Current Population Survey (CPS) Summary Statistics \label{tab:sumstat1}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lc}
\toprule
Characteristic & All Sample 
N = 318,404\\
\midrule
Female & 0.49\\
Asian & 0.65\\
Age & 8.7 
(5.1)\\
College Graduate: 
 	 Father & 0.50\\
College Graduate: 
 	 Mother & 0.48\\
Total Family Income 
 	 (1999 dollars) & 78,763 
(80,171)\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] The samples include children ages 17 and below who live in intact families. First-generation Asian immigrant children that were born in a Asian country. Native-born second-generation Asian immigrant children with at least one parent born in a Asian country. Finally, native-born third generation Asian immigrant children with native-born parents and at least one grand parent born in a Asian country.
\item[2] Data source is the 2004-2021 Current Population Survey.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\caption{Current Population Survey (CPS) Summary Statistics \label{tab:sumstat1}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lc}
\toprule
Characteristic & All Sample N = 318,404\\
\midrule
Female & 0.49\\
Asian & 0.65\\
Age & 8.4 (5.1)\\
College Graduate:  	 Father & 0.52\\
College Graduate:  	 Mother & 0.52\\
Total Family Income  	 (1999 dollars) & 87,031 (84,797)\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] The samples include children ages 17 and below who live in intact families. First-generation Asian immigrant children that were born in a Asian country. Native-born second-generation Asian immigrant children with at least one parent born in a Asian country. Finally, native-born third generation Asian immigrant children with native-born parents and at least one grand parent born in a Asian country.
\item[2] Data source is the 2004-2021 Current Population Survey.
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2024-08-24 output/tables/tab05-iat_regression_tab_byparent_type.tex
edits

\begin{table}[H]

\caption{Relationship Between Bias and Self-Reported Asian identity Among Second-Generation Asian Immigrants: By Parental Type \label{regtab-byparent-01}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{Parents Type} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{\makecell[c]{Both Parents \\ from Spanish \\ Speaking Country \\ (HH)}} & \multicolumn{1}{c}{\makecell[c]{Father \\ from Spanish \\ Speaking Country \\ (HW)}} & \multicolumn{1}{c}{\makecell[c]{Mother  \\ from Spanish \\ Speaking Country \\ (WH)}} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5}
  & \specialcell{(1) \\ $A^2_{ist}$} & \specialcell{(2) \\ $A^2_{ist}$} & \specialcell{(3) \\ $A^2_{ist}$} & \specialcell{(4) \\ $A^2_{ist}$}\\
\midrule
Bias & -0.45*** & -0.15** & -1.16*** & -0.77***\\
 & (0.09) & (0.07) & (0.23) & (0.20)\\
Female & 0.00 & 0.00 & -0.01 & 0.02\\
 & (0.00) & (0.00) & (0.01) & (0.01)\\
College Graduate: Mother & 0.01 & -0.01 & 0.06* & 0.01\\
 & (0.01) & (0.01) & (0.03) & (0.02)\\
College Graduate: Father & 0.01 & 0.01* & -0.03 & 0.01\\
 & (0.01) & (0.01) & (0.03) & (0.03)\\
\midrule
Observations & 167,709 & 103,697 & 19,982 & 44,030\\
Year $\times$ Region FE & X & X & X & X\\
Mean & 0.72 & 0.96 & 0.38 & 0.32\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of a heterogeneous effect of regression (\ref{eq:identity_reg_bias}) by 
                      type of parents with region × year fixed effects. 
                      I include controls for sex, quartic age, fraction of Asians in a state, and parental education.
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include second-generation Asian children ages 17 and below who live in intact families. 
                      Native-born second-generation Asian 
                      immigrant children with at least one parent born in a Asian 
                      country.}
\item[3] \footnotesize{Column (1) includes the results to regression (\ref{eq:identity_reg_bias}) on all second-generation immigrants, 
                                        column (2) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a father and mother that were born in a Asian country (HH),
                                        column (3) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a father that was born in a Asian country and a native-born mother (HW), and
                                        column (4) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a native-born father and a mother that was born in a Asian country (WH).}
\item[4] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Relationship Between Bias and Self-Reported Asian identity Among Second-Generation Asian Immigrants: By Parental Type \label{regtab-byparent-01}}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{Parents Type} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{\makecell[c]{Both Parents \\ from Spanish \\ Speaking Country \\ (HH)}} & \multicolumn{1}{c}{\makecell[c]{Father \\ from Spanish \\ Speaking Country \\ (HW)}} & \multicolumn{1}{c}{\makecell[c]{Mother  \\ from Spanish \\ Speaking Country \\ (WH)}} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5}
  & \specialcell{(1) \\ $A^2_{ist}$} & \specialcell{(2) \\ $A^2_{ist}$} & \specialcell{(3) \\ $A^2_{ist}$} & \specialcell{(4) \\ $A^2_{ist}$}\\
\midrule
Bias & -0.08** & -0.05 & -0.15 & -0.10\\
 & (0.03) & (0.03) & (0.10) & (0.06)\\
Female & 0.00 & -0.01 & -0.03* & 0.01\\
 & (0.00) & (0.00) & (0.02) & (0.02)\\
College Graduate: Mother & 0.01 & -0.01* & 0.10*** & 0.03\\
 & (0.01) & (0.01) & (0.03) & (0.02)\\
College Graduate: Father & 0.00 & 0.01 & -0.05** & 0.01\\
 & (0.01) & (0.01) & (0.02) & (0.03)\\
\midrule
Observations & 80,137 & 50,835 & 9,055 & 20,247\\
Year $\times$ Region FE & X & X & X & X\\
Mean & 0.73 & 0.97 & 0.39 & 0.3\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of a heterogeneous effect of regression (\ref{eq:identity_reg_bias}) by 
                      type of parents with region × year fixed effects. 
                      I include controls for sex, quartic age, fraction of Asians in a state, and parental education.
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include second-generation Asian children ages 17 and below who live in intact families. 
                      Native-born second-generation Asian 
                      immigrant children with at least one parent born in a Asian 
                      country.}
\item[3] \footnotesize{Column (1) includes the results to regression (\ref{eq:identity_reg_bias}) on all second-generation immigrants, 
                                        column (2) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a father and mother that were born in a Asian country (HH),
                                        column (3) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a father that was born in a Asian country and a native-born mother (HW), and
                                        column (4) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a native-born father and a mother that was born in a Asian country (WH).}
\item[4] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}
